Dewlap color variation in \textit{Anolis sagrei} is maintained between habitats within islands of the West Indies

### 2020-07-04 ms/sections/discussion.tex
changing location content for the ms

\paragraph{Dewlap coloration differs between habitat-types} We found that male dewlap coloration in \textit{A. sagrei} significantly varied between habitat-types (beach scrub bush, primary coppice forest and mangrove forest) on five islands of the West Indies: Abaco, Bimini, Cayman Brac, Little Cayman and Long Island. However, the habitat-specific variation in dewlaps was not consistent between these islands. Although those results are consistent with adaptation at a very local scale, other evolutionary drivers could be at work, including phenotypic plasticity, random drift, or historical contingency, including multiple colonization events. We reject this last explanation because all of the island populations in this study are strictly monophyletic, implying a single colonization event per island (van de Schoot, unpublished thesis; \citealt{Driessens2017}). While random drift cannot be completely ruled out, we see little evidence for a role of phenotypic isolation-by-distance (spatial autocorrelation) in explaining the differences we report. We did detect a significant signal of isolation-by-distance on Eleuthera, but we did not find differences in dewlap coloration between habitats on this island.

@@

\paragraph{Dewlap coloration could be locally adapted} Presently, we do not know the adaptive drivers of dewlap color divergence observed in this study. Some degree of parallel evolution is usually a good indicator for an adaptive process \citep{Losos2011}, and convergent patterns of dewlap color evolution in similar environments across islands and species have been documented in other species \citep{Thorpe2002a, Thorpe2002b}. Here, however, we found little consistency in between-habitat divergence across the nine islands studied; except maybe for dewlap brightness being lower in the primary coppice habitat on three islands, and the primary coppice habitat being intermediate in coloration between mangrove and beach scrub on two islands. Those patterns could reflect adaptation to components of the habitat \citep{Endler1988}, but it is not clear what those components of the habitat might be.\\

>>>>

\paragraph{Dewlap coloration differs between habitat-types} We found that male dewlap coloration in \textit{A. sagrei} significantly varied between habitat-types (beach scrub bush, primary coppice forest and mangrove forest) on five islands of the West Indies: Abaco, Bimini, Cayman Brac, Little Cayman and Long Island. However, the habitat-specific variation in dewlaps was not consistent between these islands. Although those results are consistent with adaptation at a very local scale, other evolutionary drivers could be at work, including phenotypic plasticity, random drift, or historical contingency, including multiple colonization events. We reject this last explanation because all of the island populations in this study are strictly monophyletic, implying a single colonization event per island (van de Schoot, unpublished thesis; \citealt{Driessens2017, Reynolds2020}). While random drift cannot be completely ruled out, we see little evidence for a role of phenotypic isolation-by-distance (spatial autocorrelation) in explaining the differences we report. We did detect a significant signal of isolation-by-distance on Eleuthera, but we did not find differences in dewlap coloration between habitats on this island.

@@

\paragraph{Dewlap coloration could be locally adapted} Presently, we do not know the adaptive drivers of dewlap color divergence observed in this study. Some degree of parallel evolution is usually a good indicator for an adaptive process \citep{Losos2011}, and convergent patterns of dewlap color evolution in similar environments across islands and species have been documented in other species \citep{Thorpe2002a, Thorpe2002b}. Here, however, we found little consistency in between-habitat divergence across the nine islands studied; except maybe for dewlap brightness being lower in the primary coppice habitat on three islands, and the primary coppice habitat being intermediate in coloration between mangrove and beach scrub on two islands. Those patterns could reflect adaptation to components of the habitat \citep{Endler1988}, but it is not clear what those components of the habitat might be. Although those patterns could reflect adaptation to components of the habitat \citep{Endler1988}, it is not clear what those components might be. Alternatively, neutral processes could produce patterns similar to local adaptation, such that this possibility cannot be completely ruled out \citep{Miles2019} (full subsection for this?).\\

### 2020-07-04 ms/sections/introduction.tex
bbl
changing location content for the ms

The staggering diversity of animal communication signals has long been of interest to evolutionary biologists. Animals use chemical, mechanical, electromagnetic, and visual signals to communicate in a wide variety of contexts, including competition for mates, species recognition, aposematism, cooperation, etc. \citep{Bradbury2011}. A primary evolutionary factor shaping communication signals is the sensory system and behavior of their recipient(s) (the sensory drive hypothesis; \citealt{Endler1988,Endler1992,Endler1998}). Over the past decades, scientists have established that signals evolve in an ecological context and are dependent on environmental conditions \citep{Endler1992,Endler1993,Endler1993a}. Just as different habitats may favor different combinations of eco-morphological traits to maximize performance and fitness \citep{Arnold1983}, they may also shape different forms of a signal, so as to maximize its transmission and detection (e.g. \citealt{Seehausen1997}), or reduce its detection by unintended recipients such as predators \citep{Endler1984,Endler1990,Endler1991,Halfwerk2014}. This selective pressure may drive the local adaptation of communication signals.\\

@@

The island bank systems of the Bahamas and Cayman Islands comprise relatively small islands, with no major geographic barriers within islands limiting dispersal for this promiscuous species \citep{Kamath2018}. These islands all share three characteristic native West Indian habitat-types -- beach scrub bush, closed-canopy primary coppice forest, and mangrove forest -- that are often spatially intermingled. These habitats contrast in environmental parameters including vegetation community, light irradiance, humidity and temperature \citep{Howard1950, Schoener1968}. Each of these islands has been colonized independently by \textit{A. sagrei} (\citealt{Driessens2017, Reynolds2020}?, van de Schoot et al. unpubl.), such that these archipelagos constitute an ideal suite of natural replicates to explore within-island dewlap diversity across multiple islands.\\

@@

Here, we analyzed the color characteristics \textit{A. sagrei} dewlaps within nine islands in the Bahamas and Cayman Islands, combining reflectance spectrometry and supervised machine learning. Our sampling design included sites in close proximity (the median distance between two sites within an island was $11.2$km). We tested the hypothesis that the spatial scale was too small for phenotypic divergence to build up. If this was not the case, we predicted that if light conditions in the environment indeed drive color evolution, dewlaps should be most similar between beach scrub and mangrove forest, which both have high levels of light irradiance, contrary to the darker, closed-canopy coppice forest. Similar, if detectability is maximized given the local conditions, we expected darker and more contrasting dewlaps in high irradiance habitats. Finally, if habitat characteristics are strong determinants of dewlap color variation, similar patterns should be observed across multiple islands \citep{Losos2011}. We found strong support for fine-scale, within-island differences in coloration between lizards inhabiting the three habitat-types in several color space dimensions, suggesting a potentially strong effect of divergent selection. However, the divergence patterns we observed did not match our expectations and were highly variable between islands. We found no evidence of isolation-by-distance as an explanation for the observed differences. Our results are nevertheless consistent with small-scale adaptive maintenance of signal polymorphism despite presumed considerable opportunity for gene flow.

>>>>

The staggering diversity of animal communication signals has long been of interest to evolutionary biologists. Animals use chemical, mechanical, electromagnetic, and visual signals to communicate in a wide variety of contexts, including, for example, competition for mates, species recognition, aposematism, and cooperation \citep{Bradbury2011}. A primary evolutionary factor shaping communication signals is the sensory system and behavior of their recipient(s) (the sensory drive hypothesis; \citealt{Endler1988,Endler1992,Endler1998}). Over the past decades, scientists have established that signals evolve in an ecological context and are dependent on environmental conditions \citep{Endler1992,Endler1993,Endler1993a}. Just as different habitats may favor different combinations of eco-morphological traits to maximize performance and fitness \citep{Arnold1983}, they may also shape different forms of a signal, so as to maximize its transmission and detection (e.g. \citealt{Seehausen1997}), or reduce its detection by unintended recipients such as predators \citep{Endler1984,Endler1990,Endler1991,Halfwerk2014}. This selective pressure may drive the local adaptation of communication signals.\\

@@

The island bank systems of the Bahamas and Cayman Islands comprise relatively small islands, with no major geographic barriers within islands limiting dispersal for this promiscuous species \citep{Kamath2018}. These islands all share three characteristic native West Indian habitat-types -- beach scrub bush, closed-canopy primary coppice forest, and mangrove forest -- that are often spatially intermingled. These habitats contrast in environmental parameters including vegetation community, light irradiance, humidity and temperature \citep{Howard1950, Schoener1968}. Each of these islands has been colonized independently by \textit{A. sagrei} (\citealt{Driessens2017, Reynolds2020}, van de Schoot et al. unpubl.), such that these archipelagos constitute an ideal suite of natural replicates to explore within-island dewlap diversity across multiple islands.\\

@@

Here, we analyzed the color characteristics \textit{A. sagrei} dewlaps within nine islands in the Bahamas and Cayman Islands, combining reflectance spectrometry and supervised machine learning. Our sampling design included sites in close proximity (the median distance between two sites within an island was $11.2$km). We tested for divergence in dewlap phenotype between habitats within islands and between islands across the range of A. sagrei. We predicted that if light conditions in the environment indeed drive color evolution, dewlaps should be most similar between beach scrub and mangrove forest, which both have high levels of light irradiance, contrary to the darker, closed-canopy coppice forest. Similar, if detectability is maximized given the local conditions, we expected darker and more contrasting dewlaps in high irradiance habitats. Finally, if habitat characteristics are strong determinants of dewlap color variation, similar patterns should be observed across multiple islands \citep{Losos2011}. We found strong support for fine-scale, within-island differences in coloration between lizards inhabiting the three habitat-types in several color space dimensions, suggesting a potentially strong effect of divergent selection. However, the divergence patterns we observed did not match our \textit{a priori} predictions and were inconsistent between islands. We found no evidence of isolation-by-distance as an explanation for the observed differences. Our results are nevertheless consistent with small-scale adaptive maintenance of signal polymorphism despite presumed considerable opportunity for gene flow.
